paper1_results_figs_slimmed_50

### 2016-03-11 paper1_results_figs_slimmed_50.Rmd
create copy of figs that produces 50% figs

---
title: "paper1_results_figs_slimmed"
output: pdf_document
#output: word_document
author: "Andy South"
date: "`r Sys.Date()`"
---

## Main Figures for paper 1 : version 3 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed.Rmd

@@

  #columns to remove from first
  indices1 <- which(names(resistPointsMix_A_T) %in% c("gen_cP0.1","gen_cP0.5","strategy"))
  #columns to add to 2nd  
  indices2 <- which(names(resistPointsMix_A_T) %in% c("gen_cP0.25"))  
  #rename column in 2nd
  tmp <- resistPointsSeq_T[indices2]
  names(tmp) <- "gen_cP0.25seq"

@@

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.25 > 500 | dif_mixA_seq$gen_cP0.25seq > 500 )

@@

  #dif_mixA_seq$mixA_minus_seq0.25 <- dif_mixA_seq["gen_cP0.25"] - dif_mixA_seq["gen_cP0.25seq"]
  dif_mixA_seq["mixA_minus_seq0.25"] <- dif_mixA_seq["gen_cP0.25"] - dif_mixA_seq["gen_cP0.25seq"]

  #TODO : later do PRCC on dif_mixA_seq["mixA_minus_seq0.25"]

@@

#names_results <- c("time_to_resistance0.5","time_to_resistance0.25","time_to_resistance0.1")
names_results <- c("time_to_resistance0.25")

@@

## Fig x2 PRCC analysis for time-to-resistance 0.25 for sequential and mixture strategies

@@

    x <- by_strategy[,1:num_inputs]
    y <- by_strategy['time_to_resistance0.25']

@@

    # print( ggdraw() + #panel_border(remove = TRUE) +
    #          draw_plot( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
    # #print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
    #          geom_point(shape=1, colour='red') +
    #          theme(axis.text.x = axis_text_x) +
    #          #theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
    #          geom_hline(yintercept = 0, linetype=3) +
    #          ylim(-1,1) +
    #          #ggtitle(paste(strategy,"PRCC")) +
    #          ggtitle(paste(strategy,"time-to-resistance 0.25")) +
    #          xlab(NULL)
    #       , height= height))

@@

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","maleExposureProp")
  out_cols <- c("time_to_resistance0.25","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

@@

    y <- 'time_to_resistance0.25'

@@

## Fig. x4 PRCC difference in time-to-resistance 0.25 between sequential and adaptive mixture strategies

@@

    x <- dif_mixA_seq[,1:num_inputs]
    y <- dif_mixA_seq["mixA_minus_seq0.25"]

@@

  ggSubset <- dif_mixA_seq
  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_diff <- abs(ggSubset$mixA_minus_seq0.25)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$abs_diff==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.25 <- 1
  df_same$seq_better_mixA0.25 <- 1
  #rbind them back onto other dataset
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mixA_not20pc_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 / ggSubset$gen_cP0.25seq <= 0.2, 1, 0 )

@@

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance slower','1'='sequential\nresistance slower'))) +

@@

             facet_grid( ~ mixA_not20pc_better_seq0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

>>>>

---
title: "paper1_results_figs_slimmed_50"
output: pdf_document
#output: word_document
author: "Andy South"
date: "`r Sys.Date()`"
---

## TRIAL VERSION OF ALL FIGS AT 50% resistance threshold

## Main Figures for paper 1 : version 4 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed_50.Rmd

@@

  #columns to remove from first
  indices1 <- which(names(resistPointsMix_A_T) %in% c("gen_cP0.1","gen_cP0.25","strategy"))
  #columns to add to 2nd  
  indices2 <- which(names(resistPointsMix_A_T) %in% c("gen_cP0.5"))  
  #rename column in 2nd
  tmp <- resistPointsSeq_T[indices2]
  names(tmp) <- "gen_cP0.5seq"

@@

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.5 > 500 | dif_mixA_seq$gen_cP0.5seq > 500 )

@@

  #dif_mixA_seq$mixA_minus_seq0.5 <- dif_mixA_seq["gen_cP0.5"] - dif_mixA_seq["gen_cP0.5seq"]
  dif_mixA_seq["mixA_minus_seq0.5"] <- dif_mixA_seq["gen_cP0.5"] - dif_mixA_seq["gen_cP0.5seq"]

  #TODO : later do PRCC on dif_mixA_seq["mixA_minus_seq0.5"]

@@

#names_results <- c("time_to_resistance0.5","time_to_resistance0.25","time_to_resistance0.1")
names_results <- c("time_to_resistance0.5")

@@

## Fig x2 PRCC analysis for time-to-resistance 0.5 for sequential and mixture strategies

@@

    x <- by_strategy[,1:num_inputs]
    y <- by_strategy['time_to_resistance0.5']

@@

    # print( ggdraw() + #panel_border(remove = TRUE) +
    #          draw_plot( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
    # #print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
    #          geom_point(shape=1, colour='red') +
    #          theme(axis.text.x = axis_text_x) +
    #          #theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
    #          geom_hline(yintercept = 0, linetype=3) +
    #          ylim(-1,1) +
    #          #ggtitle(paste(strategy,"PRCC")) +
    #          ggtitle(paste(strategy,"time-to-resistance 0.5")) +
    #          xlab(NULL)
    #       , height= height))

@@

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","maleExposureProp")
  out_cols <- c("time_to_resistance0.5","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

@@

    y <- 'time_to_resistance0.5'

@@

## Fig. x4 PRCC difference in time-to-resistance 0.5 between sequential and adaptive mixture strategies

@@

    x <- dif_mixA_seq[,1:num_inputs]
    y <- dif_mixA_seq["mixA_minus_seq0.5"]

@@

  ggSubset <- dif_mixA_seq
  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.5 <- ifelse( ggSubset$mixA_minus_seq0.5 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.5 <- ifelse( ggSubset$mixA_minus_seq0.5 < 0, 1, 0 )
  ggSubset$abs_diff <- abs(ggSubset$mixA_minus_seq0.5)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$abs_diff==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.5 <- 1
  df_same$seq_better_mixA0.5 <- 1
  #rbind them back onto other dataset
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mixA_not20pc_better_seq0.5 <- ifelse( ggSubset$mixA_minus_seq0.5 / ggSubset$gen_cP0.5seq <= 0.2, 1, 0 )

@@

             facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix\nresistance slower','1'='sequential\nresistance slower'))) +

@@

             facet_grid( ~ mixA_not20pc_better_seq0.5, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +
